Mixture Models for Single--Cell Assays with Application to Vaccine Studies

### 2012-09-14 MIMOSA.tex
updated link to MIMOSA on github

All of the results presented here were obtained with a software implementation of the EM and MCMC MIMOSA models in R and C++, and is freely available from GitHub \\
(\url{http://www.github.org/gfinak/MIMOSA}). An R package will soon be released as part of the Bioconductor project~\citep{Gentleman:2004tt}.

>>>>

All of the results presented here were obtained with a software implementation of the EM and MCMC MIMOSA models in R and C++, and is freely available from GitHub \\
(\url{http://www.github.org/RGLab/MIMOSA}). An R package will soon be released as part of the Bioconductor project~\citep{Gentleman:2004tt}.
